Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-07-11 Paper/paper.tex
added new figures

@@

\includegraphics[trim=20 0 0 0, width=1.02\columnwidth]{plots/LambdaMedian_vs_N_AstroPopulation}

@@

% \includegraphics[width=1.03\columnwidth]{plots/RelErrorLambdaMedian_vs_N.pdf}
% \includegraphics[width=1.03\columnwidth]{plots/LambdaCIWidths_vs_N.pdf}
% \caption{{\it Left}: In the main panel is shown the width of the measured $90\%$ 
% confidence interval for $\lambdans$, normalized by its true value,
%  as a function of the number of events observed $N$. In the inset, we
%  show the same measurement uncertainty, but not normalized, and on a 
%  logarithmic axis for $N$ as well.
%  From both the inset and the main plot, we find that for the first $3-4$ events
%  our measurement is prior limited. As $N$ increases, the uncertainty falls 
%  roughly as $1/\sqrt{N}$ with intermittent loud signals causing more rapid 
%  (than $1/\sqrt{N}$) narrowing of the confidence interval.
%  {\it Right}: This figure shows the fractional difference between the median
%  recovered value from the posterior probability distribution for $\lambdans$
%  as a function of $N$. Different curves correspond to different injected values
%  of $\lambdans$, and are shaded from light to dark in direct proportion. 
%  The horizontal dashed brown line marks $10\%$ deviation of the median from the 
%  true value.
% We find that within $\approx 10$ detections, the median measured value for
% $\lambdans$ would estimate the true value for the star with the remarkable 
% accuracy of $10\%$.
% \label{fig:TT_LambdaError_vs_N_L500_2000_CI90_0}
%LambdaCIWidths_vs_N_AllPopulations_Log_L

@@

\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L2000.pdf}
\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L2000.pdf}\\
\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1500.pdf}
\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L1500.pdf}\\
\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1000.pdf}
\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L1000.pdf}\\
\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L800.pdf}
\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L800.pdf}\\
\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L500.pdf}
\includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L500.pdf}

@@

% \includegraphics[width=.9\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L2000.pdf}
% \includegraphics[width=.9\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1500.pdf}\\
% \includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1000.pdf}
% \includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L800.pdf}
% \includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L500.pdf}
% \caption{ In the main panel is shown the width of the measured $90\%$ 
% confidence interval for $\lambdans$, normalized by its true value,
%  as a function of the number of events observed $N$. In the inset, we
%  show the same measurement uncertainty, but not normalized, and on a 
%  logarithmic axis for $N$ as well.
%  From both the inset and the main plot, we find that for the first $3-4$ events
%  our measurement is prior limited. As $N$ increases, the uncertainty falls 
%  roughly as $1/\sqrt{N}$ with intermittent loud signals causing more rapid 
%  (than $1/\sqrt{N}$) narrowing of the confidence interval.
% \label{fig:TT_LambdaError_vs_N_L500_2000_CI90_0}

>>>>

% \includegraphics[trim=20 0 0 0, width=1.02\columnwidth]{plots/LambdaMedian_vs_N_AllPopulation}
% \includegraphics[trim=20 0 0 0, width=1.02\columnwidth]{plots/LambdaMedian_vs_N_AstroPopulation}
% \caption{%
% {\it Left:} This figure shows the median value of the recovered
% probability distribution for $\lambdans$, as a function of the number of events
% in the population $N$. There are four family of curves, one corresponding each
% to $\lambdans=\{500,1000,1500,2000\}$, with $100$ independent populations
% within each family. One curve in each family is highlighted in color, 
% representing that it is the same population as was illustrated in
% Fig.~\ref{fig:TT_Lambda_vs_N_L800_CI90_0}-\ref{fig:TT_Lambda_vs_N_CI90_0}.
% In the same color we show $\pm 10\%$ error-bounds on $\lambdans$ with
% horizontal dash-dotted lines. We observe that within $10-25$ observations, 
% the median of the measured cumulative probability distribution for $\lambdans$
% will lie within $10\%$ of the true value.
% {\it Right:} This figure is identical to the left panel, with the only
% difference that the BH masses in each population are restricted to lie
% {\it outside} the astrophysical mass-gap (i.e. paradigm B). The difference that
% we observe under this paradigm is that we need more ($30+$) events to achieve 
% the same ($10\%$) measurement accuracy for populations with $\lambdans<1000$.
% For more deformable neutron stars, $10-25$ events would suffice.
% \label{fig:TT_LambdaMedian_vs_N_AllInOne}
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L2000.pdf}
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L2000.pdf}\\
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1500.pdf}
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L1500.pdf}\\
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1000.pdf}
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L1000.pdf}\\
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L800.pdf}
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L800.pdf}\\
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L500.pdf}
% \includegraphics[width=0.8\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L500.pdf}
% \caption{%
% These figures show the width of the $90\%$ confidence interval for $\lambdans$
% (normalized by its true value), as a function of the number of observed events
% $N$. The left column panels show populations sampled under paradigm A, which
% allows BH masses to fall within the astrophysical mass-gap, while those on the
% right show populations drawn under paradigm B which respects the mass-gap.
% Each panel corresponds to a unique value of populations' $\lambdans$,
% decreasing from $2000\rightarrow 500$ as we go from top to bottom. In each panel,
% $100$ curves are shown, each corresponding to an independent population draw. The
% one colored curve in each panel highlights the population used in
% Fig.~\ref{fig:TT_Lambda_vs_N_L800_CI90_0}-\ref{fig:TT_Lambda_vs_N_CI90_0}.
% The insets in each panel show the same information, with the ordinate {\it not}
% normalized by the true value of $\lambdans$.
% We find that with approximately $25$ or so events, we begin to put
% statistically meaningful constraints on $\lambdans$, restricting it to within
% $\pm 50\%$ of the true value. We can expect to achieve this with a few years
% of design aLIGO operation~\cite{Abadie:2010cfa}. Further tightening of the
% confidence intervals will require $40+$ events.
% \label{fig:TT_LambdaError_vs_N_L500_2000_CI90_0_AllInOne}

@@

\includegraphics[trim=20 0 0 0, width=1.02\columnwidth]{plots/LambdaMedian_vs_N_AstroPopulation}\\
\includegraphics[trim=20 0 0 0, width=1.02\columnwidth]{plots/LambdaMedian90pc_vs_N_AllPopulation}
\includegraphics[trim=20 0 0 0, width=1.02\columnwidth]{plots/LambdaMedian90pc_vs_N_AstroPopulation}\\

@@

@@

\includegraphics[width=\columnwidth]{plots/LambdaCIWidths90pc_vs_N_AllPopulation.pdf}
\includegraphics[width=\columnwidth]{plots/LambdaCIWidths90pc_vs_N_AstroPopulation.pdf}

@@
